---
title: 'Problem Set 6: Regression Discontinuity'
author: "Claire Duquennois"
output:
  html_document:
    number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
***Name:***
Kiersten Kochanowski


Instructions: 

- This assignment is an individual assignment. You may discuss your responses in small groups or reach out to a classmate if you are having difficulties with coding but your code and answers must reflect your individual efforts and be written using your own words. Identical assignments will be given a zero grade. 

- You must post your code in a private repo on GitHub and invite Neil and I as collaborators. 

- You must update your work on GitHub frequently through commits where we can observe which lines you most recently worked on when we click on the repo history. This is done very easily if you are using Git correctly which is part of what we are assessing with this assignment. Make sure you make at least five commits that highlight your most recent changes. 



# Empirical Analysis using Data from Manacorda, Miguel, & Vigorito (2011, American Economic Journal: Applied Economics)


This exercise uses data from Manacorda, Miguel, & Vigorito's paper, "Government Transfers and Political Support," published in the *American Economic Journal: Applied Economics* in 2011. This paper studies how receipt of a government anti-poverty cash transfer changes how beneficiary households support and view the government. 


# Finding the data

The data can be found on Edward Miguel's faculty website. Download and extract the contents from the `Government_Transfers_replication.zip` file. 

# Set up and constructing the data

The original data used in the paper is confidential. The authors instead provide the `reg_panes.dta` data file which is anonymized and created from the original data. 

## Question 1: Loading the Packages

Load any R packages you will be using:
**Code:**

```{r}
library(haven)
library(dplyr)
library(stargazer)
library(lfe)
library(tidyverse)
#install.packages("statar")
library(statar)
library(ggplot2)
```


## Question 2: Open the `reg_panes.dta` file. To complete this problem set you will need the following variables from this data file: 

| Name            |Description                                        |
|-----------------|---------------------------------------------------|
|aprobado         |Ever received PANES 2005-2007                      |
|untracked07      |Untracked in 2007                                 |
|h_89             |Supports current government 2007 [1 to 3]|         |
|hv34             |Supports current government 2008 [1 to 3]|         | 
|ind_reest        |Predicted Income                                   | 
|newtreat         |PANES eligibility                                  |
|geo              |Geographic locality                                |
|bl_medad         |Mean age                                           |
|lnbl_ytoth_pc    |Log per capita income                              |
|bl_hhsize        |Mean household size                                |
|bl_meduc         |Mean education                                     |
|missbl_medad     |Missing mean age                                   |
|misslnbl_ytoth_pc|Missing log per capita income                      |
|missbl_hhsize    |Missing mean household size                        |
|missbl_meduc     |Missing mean education                             |
|sexo             |Respondent is female                               |
|edad             |Respondent age                                     |
|aniosed07        |Education in 2007                                  |
|misssexo         |Missing gender                                     |
|missedad         |Missing age                                        |
|missaniosed      |Missing education                                  |


Drop all other variables. If needed, give the variables you are keeping more intuitive names. 


**Code:**
```{r}
reg_panes_orig <- read_dta("/Users/Kiersten/Documents/School/S2_Causal_Inf/PS6_Kochanowski/Data/reg_panes.dta")
View(reg_panes_orig)
reg_panes <- select(reg_panes_orig, aprobado, untracked07, h_89, hv34, ind_reest, newtreat, geo, bl_medad, lnbl_ytoth_pc, bl_hhsize, bl_meduc, missbl_medad, misslnbl_ytoth_pc,missbl_hhsize, missbl_meduc, sexo, edad, aniosed07, misssexo, missedad, missaniosed)
#View(reg_panes)
```


## **Question 3: The data as downloaded will require that you clean the variables of interest and construct a new dataset to generate the graphs. Start by generating the following cleaned variable:**

-An indicator for receiving PANES that is NA if a respondent is untracked in 2007

**Code:**
```{r}
reg_panes$treat<-0
reg_panes$treat[reg_panes$ind_reest>=0]<- 0
reg_panes$treat[reg_panes$ind_reest<0]<- 1
reg_panes$treat[reg_panes$untracked07==1]<-NA
```


## **Question 4: We are going to re-scale the variables that indicate support for the current government so that responses range from 0 to 1. To do this, tabulate the current variable to see how it is distributed and then generate a variable that will be NA if it is currently coded as 9, 0 if currently 2, 0.5 if currently 1 and 1 if currently 3. Do this for both the 2007 and 2008 variable. **

Note: This is how the authors modify this variable in their code. It seems counter intuitive and does not correspond to the description of how this variable is coded in the survey questionnaire as reported in their appendix though it does correspond to their discussion in footnote 12. My guess is the transcription/translation of the survey question is incorrect.

**Code:**
```{r}
#2007
reg_panes$sup07<-NA
reg_panes$sup07[reg_panes$h_89==1]<-0
reg_panes$sup07[reg_panes$h_89==2]<-0.5
reg_panes$sup07[reg_panes$h_89==3]<-1
reg_panes$sup07[reg_panes$h_89==9]<-NA
table(reg_panes$h_89)
table(reg_panes$sup07)

#2007
reg_panes$sup08<-NA
reg_panes$sup08[reg_panes$hv34==1]<-0
reg_panes$sup08[reg_panes$hv34==2]<-0.5
reg_panes$sup08[reg_panes$hv34==3]<-1
reg_panes$sup08[reg_panes$hv34==9]<-NA
table(reg_panes$hv34)
table(reg_panes$sup08)
```



## **Question 5: Generate a variable that is the square of predicted income.**

**Code:**
```{r}
reg_panes$ind_reest_sqd <- reg_panes$ind_reest^2
```


# We start by reproducing the main figures (2,3,and 4) of the paper as good figures are key to any regression discontinuity paper.


## **Question 6: The data consists of over 3000 observations. How many points are plotted on these figures? How should we interpret the y axis? What does each point below the threshold represent? What does each point above the threshold represent?**

- 1,935 points (households) are plotted on these figures - there are 43 households represented as the mean within each cell (bin). 
- The y-axis represents the treatment status
- The points below the threshold represent the mean treatment (1) for each income score percentile below the threshold. 
- The points above the threshold represent the mean treatment (0) for each income score percentile below the threshold.
- Overall the figure shows that the implementation of treatment was honest and "clean" where all households that qualified for treatment received treatment (given the percentile averages are consistently 1) and the households that did not qualify (above the threshold) did not receive treatment (given the percentile averages are consistently around 0)

## **Question 7: Why is the number of points above the threshold different from the number below? **

**Answer:**
The study wanted to gather more information on treatment recipient households so they split the sample between eligible and ineligible 2:1. This was likely for budget concern reasons - wanting to spend more resources on insight from the treatment group than collecting information from more households in the ineligible group.


## **Question 8: Replicating these figures will require restructuring our data and calculating the values that are plotted. Generate a variable that will indicate the percentile group the observation is in. Note the difference in the number of percentile groups above and below the threshold. **

Note: you may find the `xtile` function in R useful.

**Code:**

```{r}
#Disqualifying households with invalid responses to government support question
nrow(reg_panes)
reg_panes$incscore <- reg_panes$ind_reest
reg_panes$incscore[is.na(reg_panes$sup07)]<-NA
reg_panes$incscore[is.na(reg_panes$sup08)]<-NA
reg_panes$incscore[is.na(reg_panes$treat)]<-NA
#View(reg_panes)

#Incscore already standardized around 0 (first negative score is below threshold (i.e. treated))
```

```{r}
# Run for loop to make cuts below threshold
y <- -0.01999099

sample_below <- c()

for(i in 1:30) {
  y <- sum(y+0.00064307)
  sample_below <- c(sample_below, y)
}

# Run for loop to make cuts above threshold
x <- 0.01989200

sample_above <- c()

for(i in 1:15) {
  x <- sum(x-0.0012368)
  sample_above <- c(sample_above, x)
}

#Create cuts vector
cuts <- c(sample_below, sample_above)
print(cuts)
midpoints <- cuts[2:45]

#Create bins
reg_panes$percentiles <- cut(reg_panes$incscore, breaks = cuts, include.lowest = TRUE, right=FALSE, labels=midpoints)

```


## **Question 9: For each of the percentile groups, calculate the mean of each of the variables we will use for plotting: predicted income, receipt of PANES, support for the government in 2007, and support for the government in 2008.**

**Code:**
```{r}
#Var to represent whether observation is included in final analysis
reg_panes$exclude <- 0
reg_panes$exclude[is.na(reg_panes$percentiles)]<-1
#New data frame with only observations that qualify (valid responses to government support question)
reg_panes2 <- filter(reg_panes, exclude == "0")
#View(reg_panes2)
```


```{r}
#Calculating means
reg_panes_sharp <- reg_panes2 %>%
  group_by(percentiles) %>%
  summarize(scoremean = mean(incscore, na.rm=TRUE), treatmean = mean(aprobado, na.rm=TRUE), sup07mean = mean(sup07, na.rm=TRUE), sup08mean = mean(sup08, na.rm=TRUE))
#View(reg_panes_sharp)
```


## **Question 10: Replicate figure 2. Make the figure as clear and informative as possible. You may want to create an indicator variable for percentiles above and below the threshold. ** 

**Code:**
```{r}
reg_panes_sharp$percentiles <- as.numeric(as.character(reg_panes_sharp$percentiles))

plot1 <- ggplot(reg_panes_sharp, aes(x=percentiles, y=treatmean)) +               geom_point() + 
        geom_vline(aes(xintercept = 0)) + labs(x = "Predicted Income", y = "Treatment",
 title ="PANES Program Eligibility & Participation",
 caption = "Notes: The figure reports the proportion of households ever enrolled in PANES as a function of the standardized score (based on administrative data). The fitted plots are linear best fits on each side of the eligibility threshold")

plot1

```


## **Question 11: What is the purpose of this figure and what should we take away from it? **

**Answer:**
Overall the figure shows that the implementation of treatment was honest and "clean" where all households that qualified for treatment received treatment (given the percentile averages are consistently 1) and the households that did not qualify (above the threshold) did not receive treatment (given the percentile averages are consistently around 0)


## **Question 12: Replicate figures 3 and 4. Make these figures as clear and informative as possible.**

**Code:**
```{r}
#Line of best fit regressions
plot2 <- ggplot(reg_panes_sharp, aes(x=percentiles, y=sup07mean)) +               geom_point() + 
        geom_vline(aes(xintercept = 0)) + labs(x = "Predicted Income", y = "Government Support",
 title ="PANES Program Eligibility & Political Support for Gov't (2007)")

plot2

```
LOB code
reg_panes$runminc<-sharp$read3-0
shpestim<-felm(read4~treated+runminc+treated*runminc, sharp)
+ geom_segment(aes(x = -0.02, xend = 0, y = shpestim$coefficients[1], yend = shpestim$coefficients[1]+3*shpestim$coefficients[3]))+
         geom_segment(aes(x = -3, xend = 0, y = shpestim$coefficients[1]+ shpestim$coefficients[2]+(-3*( shpestim$coefficients[3]+
plot6shp<-ggplot(sharp_mean, aes(x=runminc, y=outbinmean))+ 
         geom_point()+
         geom_vline(xintercept = 0)+
         geom_segment(aes(x = 0, xend = 3, y = shpestim$coefficients[1], yend = shpestim$coefficients[1]+3*shpestim$coefficients[3]))+
         geom_segment(aes(x = -3, xend = 0, y = shpestim$coefficients[1]+ shpestim$coefficients[2]+(-3*( shpestim$coefficients[3]+ shpestim$coefficients[4])), yend = shpestim$coefficients[1]+ shpestim$coefficients[2]))+
  #adding some labeling for course notes:
  annotate("text", x = 0.75, y = 64.8, label = "Intercept~is~alpha~+~tau" ,parse = TRUE)+
  annotate("text", x = -0.6, y = 54, label = "Intercept~is~alpha" ,parse = TRUE)+
  annotate("text", x = -2, y = 64, label = "Slope~is~beta~+~gamma" ,parse = TRUE)+
  annotate("text", x = 2, y = 54, label = "Slope~is~beta" ,parse = TRUE) 

```{r}
plot3 <- ggplot(reg_panes_sharp, aes(x=percentiles, y=sup08mean)) +               geom_point() + 
        geom_vline(xintercept = 0) + labs(x = "Predicted Income", y = "Government Support",
 title ="PANES Program Eligibility & Political Support for Gov't (2008)")

plot3

```


## **Question 13: Interpret these figures. What should we take away from them? **

**Answer:** 


## **Question 14: Replicate the results of the three regressions estimated in the first column of table 1. Present your results in a table. Interpret the coefficients.**

**Code:**
```{r}
#reg_panes2 <- as.data.frame(reg_panes2)
#reg_panes2$incscore_sqrd <- reg_panes2$incscore^2
reg_panes <- as.data.frame(reg_panes)
reg_panes$incscore_sqrd <- reg_panes$incscore^2
View(reg_panes)

#No polynomial
r1 <- felm(data=reg_panes, aprobado ~ treat|0|0|ind_reest)
#Create clustered se for stargazer
cluster_se1 <- as.vector(summary(r1,cluster = c("ind_reest"))$coefficients[,"Cluster s.e."])

#First order polynomial
r2 <- felm(data=reg_panes, aprobado ~ treat + ind_reest|0|0|ind_reest)
#Create clustered se for stargazer
cluster_se2 <- as.vector(summary(r2,cluster = c("ind_reest"))$coefficients[,"Cluster s.e."])

#Quadratic polynomial
r3 <- felm(data=reg_panes, aprobado ~ treat + ind_reest_sqd|0|0|ind_reest)
#Create clustered se for stargazer
cluster_se3 <- as.vector(summary(r3,cluster = c("ind_reest"))$coefficients[,"Cluster s.e."])

stargazer(r1, r2, r3, type="text", header=FALSE, title="PANES Eligibility, Participation & Political Support for Government", 
                     style="qje", 
                     se = list(r1$cluster_se1, r2$cluster_se2, r3$cluster_se3),
                     covariate.labels = c("Eligibility", "Income Score", "Income Score Sqrd"),
                     dep.var.labels.include = TRUE,
                     omit = "Constant",
                     add.lines = list(c("Score controls", "None", "Linear", "Quadratic")))

```


**Answer:**
This shows that the relationship can be described with a linear regression given all coefficients are significant and robust (don't change much based on the polynomial)



## **Question 15: Write down the specifications used in row 2 of columns 1,2 and 3 of table 1. **

**Answer:**
The dependent variable is political support for the government in the first follow-up survey in 2007. These regressions only use observations with valid responses. Similar to the first row, these regressions use different parameterizations of the running variable (income score): no polynomial, first order polynomial (linear), and quadratic polynomial.



## **Question 16: Replicate all of the results reported in row 2 of Table 1. Explain the difference between these specifications and interpret their coefficients.**
Hint: the variables listed in the table above after newtreat are the controls you will want to include.

**Code:**
```{r}
#View(reg_panes2)

#No polynomial
r4 <- felm(data=reg_panes, sup07 ~ treat|0|0|ind_reest)
#Create clustered se for stargazer
cluster_se4 <- as.vector(summary(r4,cluster = c("ind_reest"))$coefficients[,"Cluster s.e."])

#First order polynomial
r5 <- felm(data=reg_panes, sup07 ~ treat + ind_reest|0|0|ind_reest)
#Create clustered se for stargazer
cluster_se5 <- as.vector(summary(r5,cluster = c("ind_reest"))$coefficients[,"Cluster s.e."])

#Quadratic polynomial
r6 <- felm(data=reg_panes, sup07 ~ treat + ind_reest_sqd|0|0|ind_reest)
#Create clustered se for stargazer
cluster_se6 <- as.vector(summary(r6,cluster = c("ind_reest"))$coefficients[,"Cluster s.e."])

stargazer(r4, r5, r6, type="text", header=FALSE, title="PANES Eligibility, Participation & Political Support for Government", 
                     style="qje", 
                     se = list(r4$cluster_se4, r5$cluster_se5, r6$cluster_se6),
                     covariate.labels = c("Eligibility", "Income Score", "Income Score Sqrd"),
                     dep.var.labels.include = TRUE,
                     omit = "Constant",
                     add.lines = list(c("Score controls", "None", "Linear", "Quadratic")))
```


**Answer:**
Coefficients not right



## **Question 17: What is the point of including all of these specifications?**

**Answer:**
These specifications show that linear regressions capture the relationship fine and we aren't representing a gap between the treatment and non-treatment groups that aren't there in reality.


## **Question 18: Using the coefficients estimated above, write out the function you would use to predict the probability a household supports the current government based on their predicted income score: **

**a) If they are eligible for the transfer using the results from column 1.**

**b) If they are not eligible for the transfer using the results from column 1.**

**c) If they are eligible for the transfer using the results from column 2.**

**d) If they are not eligible for the transfer using the results from column 2.**

**e) If they are eligible for the transfer using the results from column 3.**

**f) If they are not eligible for the transfer using the results from column 3.**

**Answer:**



## **Question 19: How narrow is the "bandwidth" used by the authors. Why does this matter? Check that the results are robust to a narrower bandwidth. **

**Code:**
```{r}

```


**Answer:**


## **Question 20: The authors attribute these effects to the causal effect of receiving the government transfers. What is the implied assumption behind this interpretation?**

**Answer:**



## **Question 21: What evidence do they provide to support this assumption?**

**Answer:**
 

## **Question 22: Was this threshold eligibility score specifically designed for this particular program? Why does this matter?**

**Answer:**





# Submission instructions:

1) Make sure the final version of your assignment is uploaded on GitHub in both html and Rmarkdown format. 




